Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-04-07 paper.tex
A little of cleanup in the discussion

\section{Discussion}
We are aware of the fact, that our communication system has to be improved until it is able to be used in allday technology. Different backscattering antennas have to be tried out to find the one with the best results. The question is mainly to which frequency the antenna has to be tuned (e.g. to the center of the TV signal or more to the edge of it). Moreover the standard \textit{RTL-SDR} antenna including the coaxial cable are of quite low quality. The antenna is e.g. too short. Hence a custom antenna would be benificial at this point as well. Moreover some fine tuning can be made when it comes to the filter coefficients of the different filters. Finally the frame structure can be optimized to be able to correct errors (e.g. Hamming code).

To come to a conclusion one can say, that we were able to show, that spectrum scanning over a huge band with sweeping is possible using the \textit{RTL-SDR}. Therupon we could provide a heat map of TV signals in a mid-sized swedish city as well as the tools to create it. And last but not least we have shown for the first time, that backscatter communication is possible with the \textit{RTL-SDR}.

>>>>

\section{Discussion}

Our system still has a lot of room for improvement.  Different
backscattering antennas could be tried to find the one with the best
combination of gain, tuning frequency and bandwidth. Moreover the
standard \textit{RTL-SDR} antenna and its coaxial cable are of low
quality.  Hence a custom antenna would be beneficial. Furthermore some
fine tuning can be made when it comes to the filter coefficients of the
different filters in the demodulator chain. Finally  errors can be
further reduced by using one of many available forward error correcting
codes.

To come to a conclusion one can say, that we were able to show, that
spectrum scanning over a huge band with sweeping is possible using the
\textit{RTL-SDR}.  This allowed us to perform a survey of the TV signal
strength in the city. And finally we have shown for the first time, that
backscatter communication is possible with the \textit{RTL-SDR}.
